Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Checkpoint comment

Figure~\ref{fig:asts} shows the number of benchmarks that can be expressed using
at most a given number of AST nodes. For a given benchmark, we found \QRESize{}
to be about half as large as \CanonizerAndSpecSize, and about a third as large
as \LensAndSpecSize{}. This demonstrates that introducing QREs saves programmers
significant effort compared to both Optician and basic Boomerang.

>>>>

Figure~\ref{fig:asts} shows the number of benchmarks that can be expressed using
at most a given number of AST nodes. For a given benchmark, we found \QRESize{}
to be about half as large as \CanonizerAndSpecSize, and about a third as large
as \LensAndSpecSize{}.\BCP{These are really the critical conclusions, and
  they are hard to see, the way the graph is drawn.  I wonder whether we
  could instead present with the individual examples on the X axis (sorted
  by number of AST nodes), with a bar above each one containing three
  regions, colored differently, for LS, CS-LS, and QC-CS...} This suggests
that introducing QREs saves programmers 
significant effort compared to both Optician and basic Boomerang.
